Read redundancies

### 2015-10-19 code/05_read_redundancy.Rmd
correct redundancy

node_redundancy %>%
	dplyr::mutate(type = interaction(type, keep)) %>%
	dplyr::group_by(net, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	tidyr::spread(robustness, n) %>%
	dplyr::mutate(critical = replace(critical, is.na(critical), 0)) %>%
	ggplot(aes(x = ordinary, z = redundant, y = critical)) +
	geom_point(aes(fill = type), shape = 21, size = 5, alpha = 0.7) + 
	facet_wrap(~ net) +
	coord_tern() + 
	scale_fill_brewer(palette = "Set1")

>>>>

node_redundancy %>%
	dplyr::mutate(type = interaction(type, keep)) %>%
	dplyr::group_by(net, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	tidyr::spread(robustness, n) %>%
	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
	ggplot(aes(x = ordinary, z = redundant, y = critical)) +
	geom_point(aes(fill = type), shape = 21, size = 5, alpha = 0.7) + 
	facet_wrap(~ net) +
	coord_tern() + 
	scale_fill_brewer(palette = "Set1")
